Gammapy: A Python package for gamma-ray astronomy

### 2023-03-03 src/ms-review.tex
Fix #99

\usepackage{graphicx}
\usepackage{url}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{import}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

@@

%% Context: development of open software
In the past decade observing the \gammaray sky has transitioned from a niche in the field of
particle physics to an established branch of astronomy, completing the view of the
sky in high energies. At the same time \textit{Python}
has become extremely popular as a scientific programming language,
in particular in the field of data sciences. This success is
mostly attributed to the simple and easy to learn syntax, the ability to act as
a "glue" language between different programming languages and last but not least
the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.

@@

%% CN: I would actually distingusih two cases here:
%% 1) the Bkg is already provided as a parametrisation
%% 2) the Bkg is not provided and, thus, has to be estimated from the obs.
After all data has been projected into the same geometry, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
these models can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the field-of-view background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the field-of-view or energy boundaries of the instrument are typically
associated with a systematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 "safe" data in the spatial as well as energy dimension.
All of these data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).

%% CN: for 1D analysis datasets, DL4 can actually be written as OGIP files,
%% so as reduced datasets in a general format, not specific to Gammapy.
%% Maybe you can briefly mention that this is due to the fact that the 1D Poisson
%% spectral analysis is liong consilidated, but this also means that Gammapy 's
%% dataset can handle lower energy data, e.g. X-ray.
%% We also said in the abstract that Gammapy is compliant with other specifications
%% adopted in high-energy astrophysics.
The counts data and the reduced IRFs in the form of maps are bundled into "datasets"
that represent the fourth data level (DL4). These reduced datasets can be written to disk,
in a format specific to \gammapy to allow users to read them back at any time later
for modeling and fitting. Different variations of such datasets support different 
analysis methods and fit statistics. The datasets can be used to perform a joint-likelihood
fit, allowing one to combine different measurements, e.g. from different observations
but also from different instruments or event classes. They can also be used for binned
simulation as well as event sampling to simulate DL3 events data.
The various DL4 objects and the associated functionalities are
implemented in the \code{gammapy.datasets} subpackage (see Section~\ref{ssec:gammapy-datasets}).

@@

\subsubsection{Region Maps}
In this case, instead of a fine spatial grid
dividing a rectangular sky region, the spatial dimension is reduced to a single
bin with an arbitrary shape, describing a region in the sky with that same
shape. Typically, they are used together with a non-spatial dimension, for
example an energy axis, to represent how a quantity varies in that dimension
inside the corresponding region. To avoid the complexity of handling
spherical geometry for regions, the regions are projected onto the local
tangential plane using a WCS transform. This approach follows Astropy's "regions"
package \citep{AstropyRegions2022}, which is both used as an API to define regions
for users as well as handling the underlying geometric operations. Region based
maps are represented by the \code{RegionGeom} and \code{RegionNDMap} classes.

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
%
\begin{figure}
	\small
	\import{code-examples/generated/}{gp_datasets}
	\caption{
        Using \code{gammapy.datasets} to read existing reduced binned datasets.
        After the different datasets are read from disk they are collected into a
        common \code{Datasets} container. All dataset types have an associated
        name attribute to allow access by name later in the code. The
        environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
        by \gammapy. The output
		of the code example is shown in Figure~\ref{fig:code_example_gp_datasets}.
    }
	\label{fig*:minted:gp_datasets}
\end{figure}
%
The \code{gammapy.datasets} subpackage contains classes to bundle
together binned data along with the associated models and likelihood function, which
provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistic, different types of Datasets are supported. The \code{MapDataset} is
used for combined spectral and morphological (3D) fitting, while a 1D spectral 
fitting can be performed using the \code{SpectrumDataset}.
While the default fit statistics for both of these classes is the \emph{Cash}~\citep{Cash}
statistic, there are other classes which support
analyses where the background is measured from control regions, so called "off" obervations.
Those require the use of a different fit statistics, which takes into account the
uncertainty of the background measurement. This case is covered by the \code{MapDatasetOnOff}
and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.

@@

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps and flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. A multiplicative correction factor (the \textit{norm})
is applied to the best fit "reference" spectral
model and is fitted in the restricted data range, defined by the 
bin group only.

@@

The sub-package also provides \texttt{matplotlib} implementations of specific
colormaps for false color image representation. Those colormaps have
been historically used by larger collaborations in the very high-energy
domain (such as \milagro or \hess) as "trademark" colormaps.
While we explicitly discourage the use of those colormaps for publication
of new results, because they do not follow modern visualization
standards, such as linear brightness gradients and accessibility
for visually impaired people, we still consider the colormaps
useful for reproducibility of past results.

@@

\subsection{1D Analysis}
\label{ssec:1d-analysis}
One of the most common analysis cases in \gammaray astronomy is measuring the
spectrum of a source in a given region defined on the sky, in conventional
astronomy also called \textit{aperture photometry}. The spectrum is typically measured
in two steps: first a parametric spectral model is fitted to the data and
secondly flux points are computed in a pre-defined set of energy bins. The
result of such an analysis performed on three simulated CTA observations is
shown in Fiure~\ref{fig:cta_galactic_center}. In this case the spectrum was
measured in a circular aperture centered on the Galactic Center, in
\gammaray~astronomy often called "ON region". For such analysis the users first
chooses a region of interest and energy binning, both defined by a
\code{RegionGeom}. In a second step, the events and the IRFs are binned
into maps of this geometry, by the \code{SpectrumDatasetMaker}. All the data and
reduced IRFs are bundled into a \code{SpectrumDataset}. To estimate
the expected background in the ON region a "reflected regions" background
method was used~\cite{Berge07}, represented in \gammapy by the
\code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
illustrated for all three observations overlayed on the counts map in Figure~\ref{fig:cta_galactic_center}.
After reduction, the data were modelled using a forward-folding method and assuming
a point source with a power law spectral shape. The model was defined, using
the \code{SkyModel} class with a \code{PowerLawSpectralModel} spectral component only.
This model was then combined with the \code{SpectrumDataset}, which contains the reduced data 
and fitted using the and \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
log-likelihood profiles are computed using the \code{FluxPointsEstimator}.

@@

\subsection{Temporal Analysis}
\label{ssec:temporal-analysis}
A common use case in most astrophysical scenarios is to study the temporal
variability of a source. The most basic way to do this is to construct a
light curve, i.e., the flux of a source in each given time bin. In \gammapy, this
is done by using the \code{LightCurveEstimator} that fits the normalisation of a
source in each time (and optionally energy) band per observation, keeping constant
other parameters.
For custom time binning, an observation needs to be split into finer time bins using
the \code{Observation.select\_time} method. Figure~\ref{fig:hess_lightcurve_pks}
shows the light curve of the blazar PKS~2155-304 in different energy bands as
observed by the \hess telescope during an exceptional flare on the night of
July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data are publicly available 
as a part of the HESS-DL3-DR1~\cite{HESS_DR1}, and shipped with
\verb"GAMMAPY_DATA". Each observation is first split into 10 min smaller
observations, and spectra extracted for each of these within a 0.11\textdegree~radius
around the source. A \code{PowerLawSpectralModel} is fit to all the datasets, leading
to a reconstructed index of $3.54 \pm 0.02$. With this adjusted spectral model
the \code{LightCurveEstimator} runs directly for two energy bands, $0.5\,{\rm TeV} - 1.5\,{\rm TeV}$,
and $1.5\,{\rm TeV} - 20\,{\rm TeV}$, respectively.
%
\begin{figure*}[t]
    \sidecaption
	\includegraphics[width=0.6666\textwidth]{figures/hess_lightcurve_pks.pdf}
	\caption{
        Binned light curves in two different energy bands for the source
        PKS~2155-304 in two energy bands ($0.5\,{\rm TeV} - 1.5\,{\rm TeV}$, and $1.5\,{\rm TeV} - 20\,{\rm TeV}$)
        as observed by the \hess telescopes in 2006. The coloured markers
        show the flux points in the different energy bands. The horizontal
        error illustrates the width of the time bin of 10~min. The vertical
        error bars show the associated asymmetrical flux errors. The marker
        is set to the center of the time bin.
    }
    \label{fig:hess_lightcurve_pks}
\end{figure*}
%
The obtained flux points can be analytically modelled using the available or
user-implemented temporal models. Alternatively, instead of  extracting a
light curve, it is also possible to directly fit temporal models to the reduced
datasets. By associating an appropriate \code{SkyModel}, consisting of both temporal
and spectral components, or using custom temporal models with spectroscopic
variability, to each dataset, a joint fit across the datasets will directly
return the best fit temporal and spectral parameters.

@@

The \iacts data reduction step is done in the same way than described in the 
previous sections but scaled up to few thousands of observations. The object
detection step typically consists in finding local maxima in the significance or TS maps,
computed by the \code{ExcessMapEstimator} or \code{TSMapEstimator} respectively.
 Further refinements can
include for example filtering and detection on these maps with techniques from
the "scikit-image" package~\citep{scikit-image}, and outlier detection from
the "scikit-learn" package~\citep{scikit-learn}. This allows e.g., to 
reduce the number of spurious detections at this stage using standard
classification algorithms and then speed up the next step
as less objects will have to be fitted simultaneously. During the modelling
step each object is alternatively fitted with different models in order to
determine their optimal parameters, and the best-candidate model. The
subpackage \code{gammapy.modeling.models} offers a large variety of choice, and the
possibility to add custom models.  Several spatial models (point-source, disk,
Gaussian...), and spectral models (power law, log parabola...) may be tested
for each object, so the complexity of the problem increases rapidly in regions
crowded with multiple extended sources. Finally an object is discarded if its
best-fit model is not significantly preferred over the null hypothesis (no
source) comparing the difference in log likelihood between these two
hypotheses.

@@

The Jupyter notebooks tutorials are generated using the sphinx-gallery
package \citep{sphinx-gallery}.
The resulting web published tutorials also provide links to playground spaces in
"myBinder"~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
on-line in versioned virtual environments hosted in the myBinder
infrastructure. Users may also play with the tutorials locally in their
laptops. They can download a specific version of the tutorials together with
the associated datasets needed and the specific conda computing environment,
using the \textit{gammapy download} command.

@@

\subsection{Proposals for Improving \gammapy}
\label{ssec:pigs}
An important part of \gammapy's development organisation is the support
for "Proposals for improving \gammapy" (PIG). This system is very much
inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}
and Astropy's APE \citep{greenfield_perry_2013} system.
PIG are self-contained documents which outline a set of larger
changes to the \gammapy code base. This includes larger feature additions,
code and package restructuring and maintenance as well as changes related
to the organisational structure of the \gammapy project. PIGs can be proposed
by any person in or outside the project and by multiple authors. They
are presented to the \gammapy developer community in a pull request
on \github and the undergo a review phase in which changes and
improvements to the document are proposed and implemented. Once the PIG
document is in a final state it is presented to the \gammapy
coordination committee, which takes the final decision on the
acceptance or rejection of the proposal. Once accepted, the proposed
change are implemented by \gammapy developers in a series of
individual contributions via pull requests. A list of all proposed
PIG documents is available in the \gammapy online documentation
\footnote{\url{https://docs.gammapy.org/dev/development/pigs/index.html}}.

A special category of PIGs are long-term "roadmaps". To develop a common
vision for all \gammapy project members on the future of the
project, the main goals regarding planned features, maintenance and
project organisation are written up as an overview and presented to the
\gammapy community for discussion. The review and acceptance process
follows the normal PIG guidelines. Typically roadmaps are written
to outline and agree on a common vision for the next long term
support release of \gammapy.

@@

	We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
	\texttt{Matplotlib} communities for providing their packages which are
	invaluable to the development of Gammapy. We thank the \github team for
	providing us with an excellent free development platform. We also are grateful
	to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
	documentation hosting and testing respectively. Α special acknowledgment has to be given
	to our first Lead Developer of \gammapy, Christoph Deil. Finally, we would like to thank
	all the \gammapy users that have provided feedback and submitted bug reports.
	J.E.~Ruiz acknowledges financial support from the State Agency for Research of
	the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the
	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709). L.~Giunti acknowledges
	financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014).

>>>>

\usepackage{graphicx}
\usepackage{url}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{import}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[autostyle]{csquotes}

@@

%% Context: development of open software
In the past decade observing the \gammaray sky has transitioned from a niche in the field of
particle physics to an established branch of astronomy, completing the view of the
sky in high energies. At the same time \textit{Python}
has become extremely popular as a scientific programming language,
in particular in the field of data sciences. This success is
mostly attributed to the simple and easy to learn syntax, the ability to act as
a \enquote{glue} language between different programming languages and last but not least
the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.

@@

%% CN: I would actually distingusih two cases here:
%% 1) the Bkg is already provided as a parametrisation
%% 2) the Bkg is not provided and, thus, has to be estimated from the obs.
After all data has been projected into the same geometry, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
these models can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the field-of-view background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the field-of-view or energy boundaries of the instrument are typically
associated with a systematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 \enquote{safe} data in the spatial as well as energy dimension.
All of these data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).

%% CN: for 1D analysis datasets, DL4 can actually be written as OGIP files,
%% so as reduced datasets in a general format, not specific to Gammapy.
%% Maybe you can briefly mention that this is due to the fact that the 1D Poisson
%% spectral analysis is liong consilidated, but this also means that Gammapy 's
%% dataset can handle lower energy data, e.g. X-ray.
%% We also said in the abstract that Gammapy is compliant with other specifications
%% adopted in high-energy astrophysics.
The counts data and the reduced IRFs in the form of maps are bundled into datasets
that represent the fourth data level (DL4). These reduced datasets can be written to disk,
in a format specific to \gammapy to allow users to read them back at any time later
for modeling and fitting. Different variations of such datasets support different 
analysis methods and fit statistics. The datasets can be used to perform a joint-likelihood
fit, allowing one to combine different measurements, e.g. from different observations
but also from different instruments or event classes. They can also be used for binned
simulation as well as event sampling to simulate DL3 events data.
The various DL4 objects and the associated functionalities are
implemented in the \code{gammapy.datasets} subpackage (see Section~\ref{ssec:gammapy-datasets}).

@@

\subsubsection{Region Maps}
In this case, instead of a fine spatial grid
dividing a rectangular sky region, the spatial dimension is reduced to a single
bin with an arbitrary shape, describing a region in the sky with that same
shape. Typically, they are used together with a non-spatial dimension, for
example an energy axis, to represent how a quantity varies in that dimension
inside the corresponding region. To avoid the complexity of handling
spherical geometry for regions, the regions are projected onto the local
tangential plane using a WCS transform. This approach follows Astropy's \textit{Regions}
package \citep{AstropyRegions2022}, which is both used as an API to define regions
for users as well as handling the underlying geometric operations. Region based
maps are represented by the \code{RegionGeom} and \code{RegionNDMap} classes.

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
%
\begin{figure}
	\small
	\import{code-examples/generated/}{gp_datasets}
	\caption{
        Using \code{gammapy.datasets} to read existing reduced binned datasets.
        After the different datasets are read from disk they are collected into a
        common \code{Datasets} container. All dataset types have an associated
        name attribute to allow access by name later in the code. The
        environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
        by \gammapy. The output
		of the code example is shown in Figure~\ref{fig:code_example_gp_datasets}.
    }
	\label{fig*:minted:gp_datasets}
\end{figure}
%
The \code{gammapy.datasets} subpackage contains classes to bundle
together binned data along with the associated models and likelihood function, which
provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistic, different types of Datasets are supported. The \code{MapDataset} is
used for combined spectral and morphological (3D) fitting, while a 1D spectral 
fitting can be performed using the \code{SpectrumDataset}.
While the default fit statistics for both of these classes is the \emph{Cash}~\citep{Cash}
statistic, there are other classes which support
analyses where the background is measured from control regions, so called \enquote{off} obervations.
Those require the use of a different fit statistics, which takes into account the
uncertainty of the background measurement. This case is covered by the \code{MapDatasetOnOff}
and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.

@@

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps and flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. A multiplicative correction factor (the \textit{norm})
is applied to the best fit reference spectral
model and is fitted in the restricted data range, defined by the 
bin group only.

@@

The sub-package also provides \texttt{matplotlib} implementations of specific
colormaps for false color image representation. Those colormaps have
been historically used by larger collaborations in the very high-energy
domain (such as \milagro or \hess) as \enquote{trademark} colormaps.
While we explicitly discourage the use of those colormaps for publication
of new results, because they do not follow modern visualization
standards, such as linear brightness gradients and accessibility
for visually impaired people, we still consider the colormaps
useful for reproducibility of past results.

@@

\subsection{1D Analysis}
\label{ssec:1d-analysis}
One of the most common analysis cases in \gammaray astronomy is measuring the
spectrum of a source in a given region defined on the sky, in conventional
astronomy also called \textit{aperture photometry}. The spectrum is typically measured
in two steps: first a parametric spectral model is fitted to the data and
secondly flux points are computed in a pre-defined set of energy bins. The
result of such an analysis performed on three simulated CTA observations is
shown in Fiure~\ref{fig:cta_galactic_center}. In this case the spectrum was
measured in a circular aperture centered on the Galactic Center, in
\gammaray~astronomy often called \enquote{on region}. For such analysis the users first
chooses a region of interest and energy binning, both defined by a
\code{RegionGeom}. In a second step, the events and the IRFs are binned
into maps of this geometry, by the \code{SpectrumDatasetMaker}. All the data and
reduced IRFs are bundled into a \code{SpectrumDataset}. To estimate
the expected background in the \enquote{on region} a \enquote{reflected regions} background
method was used~\cite{Berge07}, represented in \gammapy by the
\code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
illustrated for all three observations overlayed on the counts map in Figure~\ref{fig:cta_galactic_center}.
After reduction, the data were modelled using a forward-folding method and assuming
a point source with a power law spectral shape. The model was defined, using
the \code{SkyModel} class with a \code{PowerLawSpectralModel} spectral component only.
This model was then combined with the \code{SpectrumDataset}, which contains the reduced data 
and fitted using the and \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
log-likelihood profiles are computed using the \code{FluxPointsEstimator}.

@@

\subsection{Temporal Analysis}
\label{ssec:temporal-analysis}
A common use case in most astrophysical scenarios is to study the temporal
variability of a source. The most basic way to do this is to construct a
light curve, i.e., the flux of a source in each given time bin. In \gammapy, this
is done by using the \code{LightCurveEstimator} that fits the normalisation of a
source in each time (and optionally energy) band per observation, keeping constant
other parameters.
For custom time binning, an observation needs to be split into finer time bins using
the \code{Observation.select\_time} method. Figure~\ref{fig:hess_lightcurve_pks}
shows the light curve of the blazar PKS~2155-304 in different energy bands as
observed by the \hess telescope during an exceptional flare on the night of
July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data are publicly available 
as a part of the HESS-DL3-DR1~\cite{HESS_DR1}. Each observation is first split into 10 min smaller
observations, and spectra extracted for each of these within a 0.11\textdegree~radius
around the source. A \code{PowerLawSpectralModel} is fit to all the datasets, leading
to a reconstructed index of $3.54 \pm 0.02$. With this adjusted spectral model
the \code{LightCurveEstimator} runs directly for two energy bands, $0.5\,{\rm TeV} - 1.5\,{\rm TeV}$,
and $1.5\,{\rm TeV} - 20\,{\rm TeV}$, respectively.
%
\begin{figure*}[t]
    \sidecaption
	\includegraphics[width=0.6666\textwidth]{figures/hess_lightcurve_pks.pdf}
	\caption{
        Binned light curves in two different energy bands for the source
        PKS~2155-304 in two energy bands ($0.5\,{\rm TeV} - 1.5\,{\rm TeV}$, and $1.5\,{\rm TeV} - 20\,{\rm TeV}$)
        as observed by the \hess telescopes in 2006. The coloured markers
        show the flux points in the different energy bands. The horizontal
        error illustrates the width of the time bin of 10~min. The vertical
        error bars show the associated asymmetrical flux errors. The marker
        is set to the center of the time bin.
    }
    \label{fig:hess_lightcurve_pks}
\end{figure*}
%
The obtained flux points can be analytically modelled using the available or
user-implemented temporal models. Alternatively, instead of  extracting a
light curve, it is also possible to directly fit temporal models to the reduced
datasets. By associating an appropriate \code{SkyModel}, consisting of both temporal
and spectral components, or using custom temporal models with spectroscopic
variability, to each dataset, a joint fit across the datasets will directly
return the best fit temporal and spectral parameters.

@@

The \iacts data reduction step is done in the same way than described in the 
previous sections but scaled up to few thousands of observations. The object
detection step typically consists in finding local maxima in the significance or TS maps,
computed by the \code{ExcessMapEstimator} or \code{TSMapEstimator} respectively.
 Further refinements can
include for example filtering and detection on these maps with techniques from
the \textit{Scikit-image} package~\citep{scikit-image}, and outlier detection from
the \textit{Scikit-learn} package~\citep{scikit-learn}. This allows e.g., to 
reduce the number of spurious detections at this stage using standard
classification algorithms and then speed up the next step
as less objects will have to be fitted simultaneously. During the modelling
step each object is alternatively fitted with different models in order to
determine their optimal parameters, and the best-candidate model. The
subpackage \code{gammapy.modeling.models} offers a large variety of choice, and the
possibility to add custom models.  Several spatial models (point-source, disk,
Gaussian...), and spectral models (power law, log parabola...) may be tested
for each object, so the complexity of the problem increases rapidly in regions
crowded with multiple extended sources. Finally an object is discarded if its
best-fit model is not significantly preferred over the null hypothesis (no
source) comparing the difference in log likelihood between these two
hypotheses.

@@

The Jupyter notebooks tutorials are generated using the sphinx-gallery
package \citep{sphinx-gallery}.
The resulting web published tutorials also provide links to playground spaces in
\textit{myBinder}~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
on-line in versioned virtual environments hosted in the myBinder
infrastructure. Users may also play with the tutorials locally in their
laptops. They can download a specific version of the tutorials together with
the associated datasets needed and the specific conda computing environment,
using the \textit{gammapy download} command.

@@

\subsection{Proposals for Improving \gammapy}
\label{ssec:pigs}
An important part of \gammapy's development organisation is the support
for \textit{Proposals for improving \gammapy}(PIG). This system is very much
inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}
and Astropy's APE \citep{greenfield_perry_2013} system.
PIG are self-contained documents which outline a set of larger
changes to the \gammapy code base. This includes larger feature additions,
code and package restructuring and maintenance as well as changes related
to the organisational structure of the \gammapy project. PIGs can be proposed
by any person in or outside the project and by multiple authors. They
are presented to the \gammapy developer community in a pull request
on \github and the undergo a review phase in which changes and
improvements to the document are proposed and implemented. Once the PIG
document is in a final state it is presented to the \gammapy
coordination committee, which takes the final decision on the
acceptance or rejection of the proposal. Once accepted, the proposed
change are implemented by \gammapy developers in a series of
individual contributions via pull requests. A list of all proposed
PIG documents is available in the \gammapy online documentation
\footnote{\url{https://docs.gammapy.org/dev/development/pigs/index.html}}.

A special category of PIGs are long-term \textit{roadmaps}. To develop a common
vision for all \gammapy project members on the future of the
project, the main goals regarding planned features, maintenance and
project organisation are written up as an overview and presented to the
\gammapy community for discussion. The review and acceptance process
follows the normal PIG guidelines. Typically roadmaps are written
to outline and agree on a common vision for the next long term
support release of \gammapy.

@@

	We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
	\texttt{Matplotlib} communities for providing their packages which are
	invaluable to the development of Gammapy. We thank the \github team for
	providing us with an excellent free development platform. We also are grateful
	to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
	documentation hosting and testing respectively. Α special acknowledgment has to be given
	to our first Lead Developer of \gammapy, Christoph Deil. Finally, we would like to thank
	all the \gammapy users that have provided feedback and submitted bug reports.
	J.E.~Ruiz acknowledges financial support from the State Agency for Research of
	the Spanish MCIU through the \textit{Center of Excellence Severo Ochoa} award to the
	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709). L.~Giunti acknowledges
	financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014).
